### 2013-03-28 doc/sosp13/method.tex

\vspace{0.5ex}
\noindent{\bf IntSort:} \TODO{Write me Brandon Holt!}

>>>>

\vspace{0.5ex}
\noindent{\bf IntSort:} This sorting benchmark is taken from the NAS
Parallel Benchmark Suite~\cite{Bailey91thenas,nas3.3} and is one on
which the CrayXMT's early predecessor once held the world speed
record~\cite{TeraRecord}. The largest problem size, class ``D'', ranks two billion
uniformly distributed random integers using either a bucket or a counting sort
algorithm, depending on the strengths of the system. Bucket sort executes a greater number of loops, but is able to leverage locality and avoid communication completely in the final phase, ranking within buckets.
For these reasons, the MPI reference version and our \Grappa implementation use bucket sort.
On the other hand, the Cray XMT cannot take advantage of locality, but has an efficient compiler-supported parallel prefix sum, so it performs best using the counting sort algorithm.
